Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-02 hscc2017/paper.tex
some revision of the soundness discussion

The soundness of the model is ensured by the {\sc verify} phase. 
The {\sc synthesise} phase is only concerned with providing a candidate 
solution that is not ensured to work for any of the plant models. 
However, it is increasingly likely to be correct as the system loops 
through counterexamples. The overall result is that if a candidate solution 
is validated by the verifier, it is necessarily sound; otherwise, we may simply 
not find a valid solution in the given time. The {\sc verify} phase looks at 
two separate elements for soundness. The first corresponds to the controller fitness 
for all plant models. This phase ensures that there exists no counterexample plant 
that would create a closed-loop with unstable poles. The controller fixed word length 
is not relevant at this point since the parameters have already been chosen to fit 
this criteria (i.e., the candidate solution is FWL). The model is verified using 
the SAT solver backend in CBMC, which looks for the satisfiability of a plant 
with an unstable closed-loop. If no counterexample is found, then the controller 
is necessarily stable for all plants in the collection. The limitation of this approach 
is the data type used by the verifier to perform the evaluation. Since the actual plant 
works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, 
we need to ensure that the rounding errors in the calculations do not cause the solution 
to be unsound. For this reason the second verification phase uses interval arithmetic 
with outward rounding to ensure that these errors do not exceed critical bounds that 
could make some (or all) plant(s) unstable. This means that whilst the solution may not be complete, 
it is sound for evaluating any collection of real plants with a defined FWL controller for all of them. 
The need for two verification phases is because whereas this second phase can ensure 
the stability of all plants in the collection, it is unable to provide a counterexample.

>>>>

While the {\sc synthesise} phase searches for potentially unsound 
candidate solutions, the soundness of the model is ensured by the {\sc verify} phase.  
If a candidate solution is validated by the verifier, it is necessarily
sound.

Through its two stages, the {\sc verify} phase looks at two separate elements for
soundness.
% The first ensures that there exists no
% counterexample plant that would create a closed-loop with unstable
% poles. The fixed word length of the controller is not relevant at this
% point since the parameters have already been chosen to fit this
% criteria (i.e., the candidate solution is FWL).
The first stage ensures that no counterexample
plant with an unstable closed loop exists with % If no such
% system exists, then the controller is stable for all
% plants in the collection with
the limitations given by the data
type used by the verifier. Since the actual
plant works in the reals, whereas we use fixed/floating point
arithmetic to evaluate it, we need to ensure that the rounding errors
in the caculations do not cause the solution to be unsound.

For this reason the second verification stage uses interval arithmetic with
outward rounding to ensure that these errors do not exceed critical
bounds that could make some (or all) plant(s) unstable. This means
that whilst the solution may not be complete, it is sound for
evaluating any collection of real plants with a defined FWL controller
for all of them. We require two verification stages because,
while the second phase can ensure the stability of all plants in
the collection, it is unable to provide a counterexample.
